Incentivizing Exploration by Heterogeneous Users

### 2018-06-02 introduction.tex
addressing modeling questions

Toward that end, we model our setting as follows.
(We describe our model at a high level here,
with formal definitions given in Section~\ref{sec:prob}.)
The \ARMNUM arms and users (or \emph{agents})
are characterized by payoff-relevant
\emph{attribute} (or \emph{feature}) vectors.
Arms' attributes are a priori unknown,
and agents' attributes are drawn from a known distribution.
An agent's reward from pulling an arm is the inner product of his
vector with the arm's vector (plus noise).
When an arm is pulled, a noisy version of its attribute vector is
observed by everyone.
Agents are myopic and will pull the arm whose expected attribute
vector (based on past noisy observations) maximizes their reward.
The principal can incentivize agents to pull particular arms by
offering rewards for the specific arm.
The principal's goal is to keep the cumulative regret across all
agents small, while incurring only small total payments.
Our main theorem can be stated informally as follows:

>>>>

Toward that end, we model our setting as follows.
(We describe our model at a high level here,
with formal definitions given in Section~\ref{sec:prob}.)
The \ARMNUM arms and users (or \emph{agents})
are characterized by payoff-relevant
\emph{attribute} (or \emph{feature}) vectors.
Arms' attributes are a priori unknown,
and agents' attributes are drawn from a known distribution.
An agent's reward from pulling an arm is the inner product of his
vector with the arm's vector (plus noise).
When an arm is pulled, a noisy version of its attribute vector is
observed by everyone.
\pfedit{This models full-text product reviews on websites like Amazon, or ratings of ``service'', ``value'', and other restaurant attributes on websites like Tripadvisor.  }
Agents are myopic and will pull the arm whose expected attribute
vector (based on past noisy observations) maximizes their reward.
\pfedit{Agents' ability to effectively base decisions on all past observations models platforms' abilities to aggregate and effectively display past feedback, through simple averages of ratings and automatic summarization of full-text reviews \citep{wang2010product,liu2012movie,abulaish2009feature}.  While platforms can manipulate the display of user data, most have an incentive to be seen as truthful.}
The principal can incentivize agents to pull particular arms by
offering rewards for the specific arm.
The principal's goal is to keep the cumulative regret across all
agents small, while incurring only small total payments.
Our main theorem can be stated informally as follows:

%One example where agents give noisy observations of items’ feature vectors is restaurant reviews on TripAdvisor.  Users provide not just an overall rating, but also separate ratings for Service, Value, Food and Atmosphere.  We may treat these as our feature vector.  Platforms collect similar explicit feature vector observations whenever their users rate not just satisfaction with an item but the more granular components that contribute to it.

%As another example, consider websites like Amazon and Yelp whose users provide full-text reviews of items.  Reviews on Yelp describe a restaurants’ attributes (service, value, etc.), and reviews on Amazon similarly describe products’ attributes.  Thus, we can think of a user reading past reviews as aggregating past users’ observations of items’ feature vectors.  In this way, platforms with full-text reviews implicitly provide feature vector observations.

%As a third example, a platform with full-text reviews could run an NLP algorithm to extract features and sentiments from reviews, and then surface them to users as rated attributes.

### 2018-06-02 problem_setting.tex
addressing modeling questions

At each time $t$, a new user (or \emph{agent}) arrives,
whose feature vector (which we also call his \emph{type})
$\AgentV{t} \in \R^d$ is drawn from a known distribution \AgentDist.
Depending on context, we will identify agents with their arrival time
$t$ or their type \AgentV{t}.
When agent $t$ pulls arm $\Pull{t} := i$,
he and all future agents observe a vector
$\ObsV{t} = \ArmV{i} + \NoiseV[t]$ for arm $i$,
and his reward is $\AgentV{t} \cdot \ObsV{t}$,
i.e., agents have linear preferences.%

@@

>>>>

At each time $t$, a new user (or \emph{agent}) arrives,
whose feature vector (which we also call his \emph{type})
$\AgentV{t} \in \R^d$ is drawn from a known distribution \AgentDist.
Depending on context, we will identify agents with their arrival time
$t$ or their type \AgentV{t}.
When agent $t$ pulls arm $\Pull{t} := i$,
he and all future agents observe a vector
$\ObsV{t} = \ArmV{i} + \NoiseV[t]$ for arm $i$,
and his reward is $\AgentV{t} \cdot \ObsV{t}$,
i.e., agents have linear preferences.
\pfedit{(We are also free to create new attributes that are nonlinear transformations of existing attributes.)}

@@

\pfedit{
We assume above that the distribution $\AgentDist$ over preference vectors is known.  In practice, one would estimate this from agents' selections and the attribute estimates and offered payments on which they were based.  While we do not show it, we hypothesize that our regret guarantees only change by constants as long as our estimate of the conditional probability of pulling an arm is correct within a constant factor (our algorithm depends on this quantity).
}

% \pfedit{
% We assume above that the distribution $\AgentDist$ over preference vectors is known.
% In practice, one would estimate this from agents' selections and attribute estimates $\ArmEV{t}{i}$
% and offered payments $\Pay{t}{i}$ at the time of selection.  
% In the process of doing such an estimation procedure, one could also select nonlinear transformations of existing attributes (increasing $d$) to improve the predictive accuracy of the assumed linear model.   
% Our analysis assumes such a procedure has already been conducted.
% This assumption is most appropriate when the number of dimensions $d$ is small relative to the number of items $N$, so that the time required to estimate the distribution over preference vectors is small relative to the time required to learn about items.
% }
%\pfcomment{One modeling assumption I don't say anything about is that $\AgentDist$ is known.  I thought about adding some text saying that it can actually be estimated from user selections as we go, which is true, but it isn't clear that we can learn it much quicker than the item attributes, in general.  Another tact is to argue that our method is robust to mis-estimation of this, which seems true intuitively, but I'm not sure how to argue it here.  Probably it is possible to desgin an algorithm that learns this distribution along with item attributes.}
